\documentclass[10pt]{article}
\pagestyle{empty}
\topmargin -.75in
\textwidth 6.5in
\textheight 10in
\oddsidemargin -0.25cm 
\makeatletter
\def\@seccntformat#1{}
\makeatother

\newenvironment{myitem}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}


\begin{document}
\begin{center} 
\Large 
\textbf{Daniel Joseph Gempesaw} 
\end{center} 
\hrule 
\vspace{0.2 cm}
\normalsize
360 Pharr Rd NE Apt. 606 \hfill gempesaw@gmail.com\\
Atlanta, GA 30305 \hfill (302) 754-1231\\
\vspace{-.60 cm}

\section{Education}
\vspace{-0.25cm}
  \begin{myitem}
\item The Georgia Tech Institute of Technology, Atlanta, GA \hfill (2008 - present)
\begin{myitem}
\item Candidate for M. S. in Mechanical Engineering \hfill GPA: 3.11/4.00
\item Research Topic: Advanced Simulation Strategies for Data Center Cooling
\end{myitem}
\item University of Delaware, Newark, DE (2004 - 2008)\hfill Graduated: May 2008
\begin{myitem}
\item Honors Bachelor of Mechanical Engineering \hfill GPA: 3.859/4.000\item Honors Bachelor of Science in Mathematics
\item Minor in Physics
\item GRE Scores: Verbal: 710/800, Quantitative: 800/800, Writing: 5.5/6.0 \hfill Sept 2007
\end{myitem}
\end{myitem}

\vspace{-0.45 cm}
\section{Experience}
\vspace{-0.25cm}

\begin{myitem}
  \item QA Architect at Sharecare, Inc. - \hfill Aug 2012 - Present
  \begin{myitem}
    \item Created test framework for in-house REST API testing (Perl)
    \item Created a customizable website-functionality monitoring suite (Perl, PHP) 
  \end{myitem}

  \item Build Manager at Sharecare, Inc. - \hfill Oct 2011 - Aug 2012
  \begin{myitem}
    \item Wrote a site crawler with daily email reports on resources - aggregated reports of status codes for 1.5million urls, images, files (Perl)
    \item Complete ownership of in-house browser automation suite 
    \item Responsible for interactions between related projects across new builds
  \end{myitem}

  \item QA Engineer I at Sharecare, Inc. - \hfill Aug 2011 - Oct 2011
  \begin{myitem}
    \item Development of in-house browser automation tool 
    \item Manual QA Testing of multiple websites
  \end{myitem}
\end{myitem}

\begin{myitem}
  \item Gempesaw, Daniel and Yogendra Joshi. ``A Review of Wavelet-Based Algorithms for\hfill Oct 2010\\ 
Applications in Reduced Order Modeling of Thermal Management Systems.''
  \begin{myitem}
    \item Refereed Conference Paper presented at NATO RTO-AVT-178 Specialists' Meeting on System Level Thermal Management for Enhanced Platform Efficiency: Bucharest, Romania. 
  \end{myitem}%

  \item Senior Design Project - Shock Mitigating Marine Seat \hfill Fall 2007
  \begin{myitem}
    \item Designed a seat using advanced composite analysis to minimize weight \& optimize strength
    \item learned about composite manufacturing in a hands-on environment
  \end{myitem}
%
\item Mathematical Modeling - Rigid Hollow Cylinders at a Liquid-Air Interface \hfill Fall 2007
\begin{myitem}
su  \item Designed experiments to analyze self assembly of straws floating on water
  \item Modeled the meniscus of multiple straws interacting by using Calculus of Variations
\end{myitem}
%
\item Summer Internship at DuPont - Chestnut Run Plaza: Pump Selection Tool\hfill Summer 2007
 \begin{myitem}
  \item Created a web-based expert system for Pump Selection including web interface
  \item Gained experience with pumps, expert systems, web servers, customer interaction
 \end{myitem}
%
\item Research with Dr. Kausik Sarkar: Drops in Shear Flow \hfill Spring 2007
 \begin{myitem}
  \item Performed simulations of drops in shear flow with custom front tracking code
  \item Worked towards validating the custom code by comparing simulations
 \end{myitem}
%
\item Research with Dr. Russell Luke: The Phase Retrieval Problem\hfill Summer 2005
 \begin{myitem}
  \item Conducted research regarding the phase retrieval problem, with applications in Optics
  \item Assisted in the design of an Optics lab to perform experiments
 \end{myitem}
\end{myitem}
%
\vspace{-.55cm}
\section{Skills}
\vspace{-0.25cm}
\item I write, read, and/or use the following frequently: Perl, PHP, elisp, bash, Emacs.
\item On a less freqeunt basis, I write and read: \LaTeX, JavaScript, AJAX, HTML5, CSS, MySQL queries.
\item Read only languages and those in which I haven't recently authored: C, C++, Java/JSP/JSTL, Matlab, Maple, Microsoft Office Suite.
\subsection{Miscellaneous}
\item Typing Speed: 120 WPM
\item Limited comprehension of Spanish and Mandarin
\item Hobbies: Ultimate Frisbee, Bass guitar
%
\vfill
\hrule
% \raggedleft
% \vspace{.2 cm}
% Last updated on: December 24, 2012
\end{document}
